\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-27 to-do2.tex
add more notes on sequential timing to to-do

@@

					\item I don't see why the legislature should make a different choice just because the foreign lobby/legislature may do something in the future

@@

			\item Need to explore for first mover (home)

>>>>

			\item Results need to be modified for first mover (home)

@@

					\item Legislature (equations 7 and 8 in the draft):
						\begin{equation}
							W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
							\label{eq:lwcg}
						\end{equation}
						becomes
						\[ 
						  W_{ML}(\btn,\ga(e_b,\ve_b)) > b^* W_{ML}\left(\btn,\ga(e_b,\ve_b)\right) + (1-b^*) W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
						\]
						This can be arranged as 
						\[ 
						  W_{ML}(\btn,\ga(e_b,\ve_b)) - W_{ML}(\bta,\ga(e_b,\ve_b)) > b^* \left[ W_{ML}\left(\btn,\ga(e_b,\ve_b)\right) - W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) \right]
						\]
						This has the interesting structure that it is always true when (\ref{eq:lwcg}) is true, and is false whenever (\ref{eq:lwcg}) is false. So all the same results go through after modifying the objective function for the legislature
					\item Lobby: objective function was
					  \[
							\max_{e_b} b(e_b,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e_b,\bta)] \pi(\tau^a) - e_b
						\]
						Now it's 
						\begin{multline*}
							\max_{e_b} \left\{ b(e_b,\bta) + b^*(1-b(e_b,\bta)) \right\} \left[\pi(\tau^n) - e_n \right] + \\
							[1 - b(e_b,\bta) - b^* + b(e_b,\bta) b^*] \pi(\tau^a) - e_b
						\end{multline*}
						So the first order condition becomes 
						\begin{equation}
							\frac{\partial b(e_b,\bta)}{\partial e_b} \left[1-b^*(e_b^*,\bta)\right] \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
						\end{equation}
						I just need to check that the extra $\bta$ will not mess up any results.

@@
